### 2022-02-17 appendix_properties_of_B/appendix.tex
first draft of the whole thing! :D

\section{Properties of the DG operator \(\bs B\)}\label{sec:properties}
In this section we prove that the DG approximation \(\bs B\) conserves probability.

Recall that the coefficients \({\boldsymbol a}_{k,i}(t)\) can be used to construct an approximate solution to a differential equation at time \(t\) as \(u_{k,i}(x,t)={\boldsymbol a}_{k,i}(t)\boldsymbol \phi_k(x)\tr{}.\) For \(i\in\calS,\,k\in\mathcal K,\,r\in\mathcal N_k\), define \(\alpha_{k,i}^r(t) := a_{k,i}^r(t)\displaystyle\int_{x\in\calD_k}\phi^r_k(x)\wrt x,\) and row-vectors \(\boldsymbol \alpha_{k,i}(t)=(\alpha_{k,i}^r(t))_{r\in\mathcal N_k}\). Motivated by the fact that we may be interested in approximations of the probabilities \(\mathbb P(X(t)\in\calD_k,\varphi(t)=i)\) rather than the function \(u_{k,i}\) itself, we can pose the problem equivalently in terms of the integrals 
\[\mathbb P\left(X(t)\in\calD_k,\varphi(t)=i\right)\approx{\boldsymbol a}_{k,i}(t)\int_{x\in\calD_k}\boldsymbol \phi_k(x)\tr{}\wrt x={\boldsymbol \alpha}_{k,i}(t)\boldsymbol 1.\] 
Define
\[\boldsymbol \alpha_k(t) = (\boldsymbol \alpha_{k,i}(t))_{i\in\calS},\mbox{ and } \boldsymbol \alpha(t)=(\boldsymbol \alpha_k(t)))_{k\in\mathcal K},\]
and matrices 
\begin{align*}
\bs P_k &= \diag\left(\int_{x\in\calD_k}\phi^r_k(x)\wrt x\right)_{ r\in\mathcal N_k},\, k\in\mathcal K^\circ,
\\\bs P &=\left[\begin{array}{ccc}
		\bs I_{N_{|\calS|}}\otimes \bs P_0 & &\\
		& \ddots &\\
		& & \bs I_{N_{|\calS|}}\otimes \bs P_K
	\end{array}\right].
\end{align*}
By choosing the basis \(\{\phi_{k}^r\}_{r\in\mathcal N_k,k\in\mathcal K^\circ}\) such that \(\int_{x\in\calD_k}\phi^r_k(x)\wrt x\neq 0\) for all \(r,k\), then \(\bs P\) is invertible. This is the case for the Lagrange polynomials, but not, for example, for the Legendre polynomials. We can (loosely) interpret the new coefficients \(\alpha_{k,i}^r(t)\) as representing the amount of probability captured by the basis function \(\phi^r_k(x)\) in phase \(i\).

The differential equation (\ref{eqn: DG ODE w BCs}) can be equivalently expressed as 

@@

 \\ {  {\mathfrak{\bs B}}}^{0{-1}} &:=-\left[c_ip_{ij}^{-1}\mathbb 1_{(c_i<0)}\right]_{i\in\calS,j\in\calS_{{-1}}}\otimes \bs P_0^{-1}\boldsymbol \phi_0(0)\tr{},

@@

 \\ {  {\mathfrak{\bs B}}}^{K {K+1}} &:= \left[c_ip_{ij}^{K+1}\mathbb 1_{(c_i>0)}\right]_{i\in\calS,j\in\calS_{K+1}} \otimes  \bs P_K^{-1} \boldsymbol\phi_K(b)\tr{},

@@

    	T_{ii}\bs I_{N_k} + c_i\bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k & i = j, \\
	T_{ij}\bs I_{N_k} & i \neq j,

@@

	\bs 0_{N_k} & i \neq j,

@@

     {  {\mathfrak{\bs B}}}^{kk}%&=\left[\begin{array}{ccc}T_{11}I_{N_k} + c_1P_k^{-1}(F_1^{kk}+G_k)M_k^{-1}P_k & T_{12}I_{N_k} & T_{1N_\calS}I_{N_k}  \\ T_{21}I_{N_k} & & \\ \vdots &\ddots & \vdots \\ & &   T_{N_\calS-1,N_\calS}I_{N_k} \\  T_{N_\calS1}I_{N_k} &  T_{N_\calS,N_\calS-1}I_{N_k} & T_{N_\calS,N_\calS}I_{N_k} +c_{N_\calS}P_k^{-1}(F_{N_\calS}^{kk}+G_k)M_k^{-1}P_k\end{array}\right]

@@

%    &=:\left[\begin{array}{ccc} {  {\mathfrak B}}_{11}^{kk} &  {  {\mathfrak B}}^{kk}_{12} &  {  {\mathfrak B}}^{kk}_{1N_\calS}  \\  {  {\mathfrak B}}^{kk}_{21} & & \\ \vdots &\ddots & \vdots \\ & &    {  {\mathfrak B}}^{kk}_{N_\calS-1,N_\calS} \\   {  {\mathfrak B}}^{kk}_{N_\calS1} &   {  {\mathfrak B}}^{kk}_{N_\calS,N_\calS-1} &  {  {\mathfrak B}}^{kk}_{N_\calS,N_\calS} \end{array}\right], 

@@

    &=:\left[\begin{array}{ccc} {  {\mathfrak{\bs B}}}_{11}^{kk} &  \hdots &  {  {\mathfrak{\bs B}}}^{kk}_{1N_\calS}  \\ \vdots &\ddots & \vdots \\   {  {\mathfrak{\bs B}}}^{kk}_{N_\calS1} &  \hdots &  {  {\mathfrak{\bs B}}}^{kk}_{N_\calS,N_\calS} \end{array}\right], \mbox{ for \(k\in\mathcal K^\circ\),}

@@

\\ {  {\mathfrak{\bs B}}}^{k,k+1}%&=\left[\begin{array}{ccc}c_1P_k^{-1}F_1^{k,k+1}M_{k+1}^{-1}P_{k+1}&  & \\  &\ddots &  \\ & &   \\  &  &c_{N_\calS}P_k^{-1}F_{N_\calS}^{k,k+1}M_{k+1}^{-1}P_{k+1} \end{array}\right] 

@@

&=:\left[\begin{array}{ccc} {  {\mathfrak{\bs B}}}^{k,k+1}_{1,1}& \hdots &  {  {\mathfrak{\bs B}}}^{k,k+1}_{1,N_\calS}\\  \vdots &\ddots & \vdots \\  {  {\mathfrak{\bs B}}}^{k,k+1}_{N_\calS,1} & \hdots & {  {\mathfrak{\bs B}}}^{k,k+1}_{N_\calS,N_\calS} \end{array}\right],\mbox{ for \(k=0,1,\dots K-1\),}

@@

\\ {  {\mathfrak{\bs B}}}^{k,k-1}%&=\left[\begin{array}{ccc}c_1P_k^{-1}F_1^{k,k-1}M_{k-1}^{-1}P_{k-1}&  & \\  &\ddots &  \\  &  &c_{N_\calS}P_k^{-1}F_{N_\calS}^{k,k-1}M_{k-1}^{-1}P_{k-1} \end{array}\right]

@@

&=:\left[\begin{array}{ccc} {  {\mathfrak{\bs B}}}^{k,k-1}_{1,1}& \hdots &  {  {\mathfrak{\bs B}}}^{k,k-1}_{1,N_\calS}\\  \vdots &\ddots & \vdots \\  {  {\mathfrak{\bs B}}}^{k,k-1}_{N_\calS,1} & \hdots & {  {\mathfrak{\bs B}}}^{k,k-1}_{N_\calS,N_\calS} \end{array}\right], \mbox{ for \(k=1,2,\dots K\).}

@@

	\begin{rem}
	One may recognise the structure of \( {  {\mathfrak{\bs B}}}\) as the structure of a quasi-birth-and-death process (QBD), with levels \(k\in\mathcal K^\circ\). This raises the question of whether \( {  {\mathfrak{\bs B}}}\) is indeed a representation of the generator matrix of a QBD, or QBD-like process. In the case of a constant basis function on each cell, i.e.~\(N_k=1\) and \(\phi_k^1(x)\propto1\), \(k\in\mathcal K^\circ\), then \( {  {\mathfrak{\bs B}}}\) is the generator of a QBD: it has zero row-sums, negative diagonal entires, and non-negative off-diagonal entries, the QBD-phase variable is \(\{\varphi_t\}\) and the level is \(k\in\mathcal K\). In fact, if \(\Delta_k\) is the same for every \(k\in\mathcal K^\circ\), then this is the same QBD discretisation of a stochastic fluid process analysed by \cite{bo2013}. However, for higher-degree polynomials \(\mathfrak{\bs B}\) is not necessarily the generator of a QBD process. We conjecture that, using polynomial basis functions, then \(N_k=1\) and \(\phi_k^1(x)\propto1\), \(k\in\mathcal K^\circ\) is the only DG approximation which has an interpretation as a QBD-like process -- not even as a QBD-RAP \citep{bn2010}.
	\end{rem}

	In the following lemma, we use the following properties of the Lagrange interpolating polynomials defined by the Gauss-Lobatto quadrature nodes. 
	\paragraph{Property 1} \(\displaystyle\sum_{s=1}^{N_k} \phi_k^s(x) = \begin{cases} 1&x\in\calD_k,\\ 0 & x\notin \calD_k.\end{cases}\)

	For \(k\in\mathcal K^\circ\), let \(\boldsymbol e_n^k\) be a row-vector of length \(N_k\) with a 1 in the \(n\)th position and zeros elsewhere.
	\paragraph{Property 2} At the cell edges, \(\bs \phi_k(y_k) = \bs e_1^k\) and \(\bs\phi_k(y_{k+1})=\bs e_{N_k}^k\), \(k\in\mathcal K^\circ\).

\begin{lem}
	If \(\{\phi^r_k(x)\}_{r\in\mathcal N_k}\), are chosen as the Lagrange interpolating polynomials on \(\mathcal D_k\), \(k\in\mathcal K^\circ\), then the matrix \( {  {\mathfrak{\bs B}}}\) has zero row-sums. 
\end{lem}
\begin{proof}
	First we make numerous algebraic observations. Let \(\boldsymbol 1\) and \(\boldsymbol 0\) be column vectors of ones and zeros, respectively, with an appropriate length depending on the context. Using Property 1, observe that 
	\begin{align*}
        \bs M_k\boldsymbol 1 &= \left(\sum_{s=1}^{N_k} \int_{x\in\calD_k}\phi^r_k(x)\phi_s^k(x)\wrt x\right)_{r\in\mathcal N_k}\tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\sum_{s=1}^{N_k} \phi_s^k(x)\wrt x \right)_{r\in\mathcal N_k} \tr{}
        %
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\wrt x\right)_{r\in\mathcal N_k} \tr{}
        %
        \\&= \bs P_k\boldsymbol 1,
	\end{align*}
	hence \(\bs M_k^{-1}\bs P_k\boldsymbol 1=\boldsymbol 1\). Also, 
	\begin{align*}
        \bs G_k\bs M_k^{-1}\bs P_k\boldsymbol 1 = \bs G_k\boldsymbol 1 &= \left(\sum_{s=1}^{N_k} \int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}\phi_k^s(x)\wrt x\right)_{r\in\mathcal N_k} \tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}\sum_{s=1}^{N_k} \phi_k^s(x)\wrt x \right)_{r\in\mathcal N_k} \tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}1\wrt x\right)_{r\in\mathcal N_k} \tr{}
	%
        \\&= \boldsymbol 0,
	\end{align*}
	where we have again used Property 1. Consider \(c_i>0\) and let \(\boldsymbol b\) and \(\boldsymbol d\) be arbitrary row-vectors of length \(N_k\) and \(N_{k+1}\), respectively. By Property 2, for \(k\in\mathcal K^\circ,\)
	\begin{align*}
        \bs F_i^{kk}\boldsymbol b &= -\boldsymbol \phi_k(y_{k+1})\tr{} \boldsymbol \phi_k(y_{k+1})\boldsymbol b \\&= -(\bs e^k_{N_k})\tr{} \bs e_{N_k}^k\bs b \\&= -b_{N_k}(\boldsymbol e_{N_k}^k)\tr{},
        %
        \\\bs F_i^{k,k+1}\boldsymbol d &= \boldsymbol \phi_{k}(y_{k+1})\tr{} \boldsymbol \phi_{k+1}(y_{k+1})\boldsymbol d \\&= (\bs e^{k}_{N_k})\tr{} \bs e_{1}^{k+1}\bs d \\&= d_{1}(\boldsymbol e_{N_{k}}^{k})\tr{}.
	\end{align*}
	Hence, observe that 
	\begin{align*}
		&\bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1} \bs P_k \bs 1 = \bs P_k^{-1} \bs \phi_k(y_k)'\bs 1 = -\bs P_k^{-1}\bs F_i^{k,k+1} \bs M_k^{-1} \bs P_k \bs 1 = - \bs P_k^{-1}(\bs e_{N_k}^k)',
	\end{align*}
	for \(k=0,1,\dots,K-1\). 
	Similarly, for \(c_i<0\), 
	\begin{align*}
		&\bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1} \bs P_k \bs 1 = \bs P_k^{-1} \bs \phi_k(y_{k+1})'\bs 1 = -\bs P_k^{-1}\bs F_i^{k,k-1} \bs M_k^{-1} \bs P_k \bs 1 = - \bs P_k^{-1}(\bs e_{1}^k)',
	\end{align*}
	for \(k=1,\dots,K\).

>>>>

\chapter{Properties of the DG operator \(\bs B\)\label{sec:properties}}
In this section we prove that the DG approximation \(\bs B\) conserves probability.

Recall that the coefficients \({\boldsymbol a}_{k,i}(t)\) can be used to construct an approximate solution to a differential equation at time \(t\) as \(u_{k,i}(x,t)={\boldsymbol a}_{k,i}(t)\boldsymbol \phi_k(x)\tr{}.\) For \(i\in\calS,\,k\in\mathcal K,\,r\in\{1,...,p_k\}\), define \(\alpha_{k,i}^r(t) := a_{k,i}^r(t)\displaystyle\int_{x=y_k}^{y_{k+1}}\phi^r_k(x)\wrt x,\) and row-vectors \(\boldsymbol \alpha_{k,i}(t)=(\alpha_{k,i}^r(t))_{r\in\{1,...,p_k\}}\). Motivated by the fact that we may be interested in approximations of the probabilities \(\mathbb P(X(t)\in\calD_{k,i},\varphi(t)=i)\) rather than the function \(u_{k,i}\) itself, we can pose the problem equivalently in terms of the integrals 
\[\mathbb P\left(X(t)\in\calD_{k,i},\varphi(t)=i\right)\approx{\boldsymbol a}_{k,i}(t)\int_{x\in\calD_{k,i}}\boldsymbol \phi_k(x)\tr{}\wrt x={\boldsymbol \alpha}_{k,i}(t)\boldsymbol 1.\] 
Define
\[\boldsymbol \alpha_k(t) = (\boldsymbol \alpha_{k,i}(t))_{i\in\calS},\mbox{ and } \boldsymbol \alpha(t)=(\boldsymbol \alpha_k(t)))_{k\in\mathcal K},\]
and matrices 
\begin{align*}
\bs P_k &= \diag\left(\int_{x=y_k}^{y_{k+1}}\phi^r_k(x)\wrt x\right)_{ r\in\{1,...,p_k\}},\, k\in\mathcal K^\circ,
\\\bs P &=\left[\begin{array}{ccc}
		\bs I_{N}\otimes \bs P_0 & &\\
		& \ddots &\\
		& & \bs I_{N}\otimes \bs P_K
	\end{array}\right].
\end{align*}
By choosing the basis \(\{\phi_{k}^r\}_{r\in\{1,...,p_k\},k\in\mathcal K^\circ}\) such that \(\int_{x=y_k}^{y_{k+1}}\phi^r_k(x)\wrt x\neq 0\) for all \(r,k\), then \(\bs P\) is invertible. This is the case for the Lagrange polynomials, but not, for example, for the Legendre polynomials. We can (loosely) interpret the new coefficients \(\alpha_{k,i}^r(t)\) as representing the amount of probability captured by the basis function \(\phi^r_k(x)\) in phase \(i\).

The differential equation~(\ref{eqn: DG ODE w BCs}) can be equivalently expressed as 

@@

 \\ {  {\mathfrak{\bs B}}}^{0{-1}} &:=-\left[c_ip_{ij}^{-1} 1{(c_i<0)}\right]_{i\in\calS,j\in\calS_{{-1}}}\otimes \bs P_0^{-1}\boldsymbol \phi_0(0)\tr{},

@@

 \\ {  {\mathfrak{\bs B}}}^{K {K+1}} &:= \left[c_ip_{ij}^{K+1} 1{(c_i>0)}\right]_{i\in\calS,j\in\calS_{K+1}} \otimes  \bs P_K^{-1} \boldsymbol\phi_K(b)\tr{},

@@

    	T_{ii}\bs I_{p_k} + c_i\bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k & i = j, \\
	T_{ij}\bs I_{p_k} & i \neq j,

@@

	\bs 0_{p_k} & i \neq j,

@@

     {  {\mathfrak{\bs B}}}^{kk}%&=\left[\begin{array}{ccc}T_{11}I_{p_k} + c_1P_k^{-1}(F_1^{kk}+G_k)M_k^{-1}P_k & T_{12}I_{p_k} & T_{1N}I_{p_k}  \\ T_{21}I_{p_k} & & \\ \vdots &\ddots & \vdots \\ & &   T_{N-1,N}I_{p_k} \\  T_{N1}I_{p_k} &  T_{N,N-1}I_{p_k} & T_{N,N}I_{p_k} +c_{N}P_k^{-1}(F_{N}^{kk}+G_k)M_k^{-1}P_k\end{array}\right]

@@

%    &=:\left[\begin{array}{ccc} {  {\mathfrak B}}_{11}^{kk} &  {  {\mathfrak B}}^{kk}_{12} &  {  {\mathfrak B}}^{kk}_{1N}  \\  {  {\mathfrak B}}^{kk}_{21} & & \\ \vdots &\ddots & \vdots \\ & &    {  {\mathfrak B}}^{kk}_{N-1,N} \\   {  {\mathfrak B}}^{kk}_{N1} &   {  {\mathfrak B}}^{kk}_{N,N-1} &  {  {\mathfrak B}}^{kk}_{N,N} \end{array}\right], 

@@

    &=:\left[\begin{array}{ccc} {  {\mathfrak{\bs B}}}_{11}^{kk} &  \hdots &  {  {\mathfrak{\bs B}}}^{kk}_{1N}  \\ \vdots &\ddots & \vdots \\   {  {\mathfrak{\bs B}}}^{kk}_{N1} &  \hdots &  {  {\mathfrak{\bs B}}}^{kk}_{N,N} \end{array}\right], \mbox{ for \(k\in\mathcal K^\circ\),}

@@

\\ {  {\mathfrak{\bs B}}}^{k,k+1}%&=\left[\begin{array}{ccc}c_1P_k^{-1}F_1^{k,k+1}M_{k+1}^{-1}P_{k+1}&  & \\  &\ddots &  \\ & &   \\  &  &c_{N}P_k^{-1}F_{N}^{k,k+1}M_{k+1}^{-1}P_{k+1} \end{array}\right] 

@@

&=:\left[\begin{array}{ccc} {  {\mathfrak{\bs B}}}^{k,k+1}_{1,1}& \hdots &  {  {\mathfrak{\bs B}}}^{k,k+1}_{1,N}\\  \vdots &\ddots & \vdots \\  {  {\mathfrak{\bs B}}}^{k,k+1}_{N,1} & \hdots & {  {\mathfrak{\bs B}}}^{k,k+1}_{N,N} \end{array}\right],\mbox{ for \(k=0,1,\dots K-1\),}

@@

\\ {  {\mathfrak{\bs B}}}^{k,k-1}%&=\left[\begin{array}{ccc}c_1P_k^{-1}F_1^{k,k-1}M_{k-1}^{-1}P_{k-1}&  & \\  &\ddots &  \\  &  &c_{N}P_k^{-1}F_{N}^{k,k-1}M_{k-1}^{-1}P_{k-1} \end{array}\right]

@@

&=:\left[\begin{array}{ccc} {  {\mathfrak{\bs B}}}^{k,k-1}_{1,1}& \hdots &  {  {\mathfrak{\bs B}}}^{k,k-1}_{1,N}\\  \vdots &\ddots & \vdots \\  {  {\mathfrak{\bs B}}}^{k,k-1}_{N,1} & \hdots & {  {\mathfrak{\bs B}}}^{k,k-1}_{N,N} \end{array}\right], \mbox{ for \(k=1,2,\dots K\).}

@@

	\begin{rem}
	One may recognise the structure of \( {  {\mathfrak{\bs B}}}\) as the structure of a quasi-birth-and-death process (QBD), with levels \(k\in\mathcal K^\circ\). This raises whether \( {  {\mathfrak{\bs B}}}\) is indeed a representation of the generator matrix of a QBD, or QBD-like process. In the case of a constant basis function on each cell, i.e.~\(p_k=1\) and \(\phi_k^1(x)\propto1\), \(k\in\mathcal K^\circ\), then \( {  {\mathfrak{\bs B}}}\) is the generator of a QBD: it has zero row-sums, negative diagonal entries, and non-negative off-diagonal entries, the QBD-phase variable is \(\{\varphi(t)\}\) and the level is \(k\in\mathcal K\). In fact, if \(\Delta_k\) is the same for every \(k\in\mathcal K^\circ\), then this is the same QBD discretisation of a stochastic fluid process analysed by \cite{bo2013}. However, for higher-degree polynomials \(\mathfrak{\bs B}\) is not necessarily the generator of a QBD process. We conjecture that, using polynomial basis functions, then \(p_k=1\) and \(\phi_k^1(x)\propto1\), \(k\in\mathcal K^\circ\) is the only DG approximation which has an interpretation as a QBD-like process -- not even as a QBD-RAP \citep{bn2010}.
	\end{rem}

	For simplicity, define \(\calD_k=[y_k,y_{k+1}]\). In the following lemma, we use the following properties of the Lagrange interpolating polynomials defined by the Gauss-Lobatto quadrature nodes. 
	\paragraph{Property 1} \(\displaystyle\sum_{s=1}^{p_k} \phi_k^s(x) = \begin{cases} 1&x\in\calD_k,\\ 0 & x\notin \calD_k.\end{cases}\)

	For \(k\in\mathcal K^\circ\), let \(\boldsymbol e_n^k\) be a row-vector of length \(p_k\) with a 1 in the \(n\)th position and zeros elsewhere.
	\paragraph{Property 2} At the cell edges, \(\bs \phi_k(y_k) = \bs e_1^k\) and \(\bs\phi_k(y_{k+1})=\bs e_{p_k}^k\), \(k\in\mathcal K^\circ\).

\begin{lem}
	If \(\{\phi^r_k(x)\}_{r\in\{1,...,p_k\}}\), are chosen as the Lagrange interpolating polynomials on \(\mathcal D_k\), \(k\in\mathcal K^\circ\), then the matrix \( {  {\mathfrak{\bs B}}}\) has zero row-sums. 
\end{lem}
\begin{proof}
	First we make numerous algebraic observations. Let \(\boldsymbol 1\) and \(\boldsymbol 0\) be column vectors of ones and zeros, respectively, with an appropriate length depending on the context. Using Property 1, observe that 
	\begin{align*}
        \bs M_k\boldsymbol 1 &= \left(\sum_{s=1}^{p_k} \int_{x\in\calD_k}\phi^r_k(x)\phi_s^k(x)\wrt x\right)_{r\in\{1,...,p_k\}}\tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\sum_{s=1}^{p_k} \phi_s^k(x)\wrt x \right)_{r\in\{1,...,p_k\}} \tr{}
        %
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\wrt x\right)_{r\in\{1,...,p_k\}} \tr{}
        %
        \\&= \bs P_k\boldsymbol 1,
	\end{align*}
	hence \(\bs M_k^{-1}\bs P_k\boldsymbol 1=\boldsymbol 1\). Also, 
	\begin{align*}
        \bs G_k\bs M_k^{-1}\bs P_k\boldsymbol 1 = \bs G_k\boldsymbol 1 &= \left(\sum_{s=1}^{p_k} \int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}\phi_k^s(x)\wrt x\right)_{r\in\{1,...,p_k\}} \tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}\sum_{s=1}^{p_k} \phi_k^s(x)\wrt x \right)_{r\in\{1,...,p_k\}} \tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}1\wrt x\right)_{r\in\{1,...,p_k\}} \tr{}
	%
        \\&= \boldsymbol 0,
	\end{align*}
	where we have again used Property 1. Consider \(c_i>0\) and let \(\boldsymbol b\) and \(\boldsymbol d\) be arbitrary row-vectors of length \(p_k\) and \(p_{k+1}\), respectively. By Property 2, for \(k\in\mathcal K^\circ,\)
	\begin{align*}
        \bs F_i^{kk}\boldsymbol b &= -\boldsymbol \phi_k(y_{k+1})\tr{} \boldsymbol \phi_k(y_{k+1})\boldsymbol b \\&= -(\bs e^k_{p_k})\tr{} \bs e_{p_k}^k\bs b \\&= -b_{p_k}(\boldsymbol e_{p_k}^k)\tr{},
        %
        \\\bs F_i^{k,k+1}\boldsymbol d &= \boldsymbol \phi_{k}(y_{k+1})\tr{} \boldsymbol \phi_{k+1}(y_{k+1})\boldsymbol d \\&= (\bs e^{k}_{p_k})\tr{} \bs e_{1}^{k+1}\bs d \\&= d_{1}(\boldsymbol e_{N_{k}}^{k})\tr{}.
	\end{align*}
	Hence, observe that 
	\begin{align*}
		&\bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1} \bs P_k \bs 1 = \bs P_k^{-1} \bs \phi_k(y_k)'\bs 1 = -\bs P_k^{-1}\bs F_i^{k,k+1} \bs M_k^{-1} \bs P_k \bs 1 = - \bs P_k^{-1}(\bs e_{p_k}^k)',
	\end{align*}
	for \(k=0,1,\dots,K-1\). 
	Similarly, for \(c_i<0\), 
	\begin{align*}
		&\bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1} \bs P_k \bs 1 = \bs P_k^{-1} \bs \phi_k(y_{k+1})'\bs 1 = -\bs P_k^{-1}\bs F_i^{k,k-1} \bs M_k^{-1} \bs P_k \bs 1 = - \bs P_k^{-1}(\bs e_{1}^k)',
	\end{align*}
	for \(k=1,\dots,K\).

	Now, with the above observations made, we first claim that, for \(c_i>0\), and \(k=0,1,...,K-1\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk+1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_k^{-1}\bs P_k\boldsymbol 1 
		\\&=\bs 0.
	\end{align*}
	The first sum is zero since \(\bs T\) is a generator of a continuous-time Markov chain. This leaves the other two terms, which, using our observations, we get 
	\begin{align*}
		& c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1
		\\&= c_i \bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1 
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i>0\) and \(k=K\), 
	\begin{align*}
		&\sum_{j\in\calS}\mathfrak{\bs B}^{KK}_{ij}\bs 1 + \mathfrak{\bs B}^{K{K+1}}_{ij}\bs 1
		\\&= \sum_{j\in\calS}T_{ij}\bs I_{N_K}\bs 1-\sum_{j\in\calS_-} c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 -\sum_{j\in\calS_{{K+1} }}c_ip_{ij}^{K+1} \bs P_K^{-1}\boldsymbol \phi_K(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_K^{-1}(\bs F_i^{KK}+\bs G_K)\bs M_K^{-1}\bs P_K\boldsymbol 1 
		\\&= -\sum_{j\in\calS_-} c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 
		\\&{}\quad-\sum_{j\in\calS_{{K+1}}}c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\bs 1+ c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1
		\\&\quad{}+ c_i \bs P_K^{-1}\bs G_K\bs M_K^{-1}\bs P_K\boldsymbol 1
		%
		\\&= - c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 + c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1 + c_i \bs P_K^{-1}\bs G_K\boldsymbol 1
		\\&= \bs 0.
	\end{align*}
	% Similarly, for \(c_i<0\), and row-vectors \(\boldsymbol b\) and \(\boldsymbol d\) of length \(p_k\) and \(N_{k-1}\), respectively, 
	% \begin{align*}
	% 	\bs F_i^{kk}\boldsymbol b &= \boldsymbol \phi^k(y_{k})\tr{} \boldsymbol \phi^k(y_{k})\boldsymbol b \\&= (\bs e^{k}_{1})\tr{} \bs e_{1}^{k}\bs b  \\&= b_{1}(\boldsymbol e_{1}^k)\tr{} 
	% 	%
	% 	\\\bs F_i^{k,k-1}\boldsymbol d &= -\boldsymbol \phi^{k}(y_{k})\tr{} \boldsymbol \phi^{k-1}(y_{k})\boldsymbol d \\&= -(\bs e^{k}_{1})\tr{} \bs e_{N_{k-1}}^{k-1}\bs d \\&= -d_{N_{k-1}}(\boldsymbol e_{1}^k)\tr{}.
	% 	\end{align*}

		Similarly, for \(c_i<0\) and \(k=1,...,K\), using the same arguments as before we have
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk-1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\bs M_k^{-1}\bs P_k\boldsymbol 1
		% \\&= \boldsymbol 0 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k-1}^{-1}\bs P_{k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}\bs F_i^{kk}\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\boldsymbol e_{1}^k)\tr{} + \boldsymbol 0 + c_i \bs P_k^{-1}(-\boldsymbol e_{1}^k)\tr{}
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i<0\) and \(k=K\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{00}_{ij}\bs 1 + \mathfrak{\bs B}^{0{-1}}_{ij}\bs 1
		&= \sum_{j\in\calS}T_{ij}\bs I_{N_0}\bs 1-\sum_{j\in\calS_+} c_ip_{ij}^{-1} \bs P_0^{-1}\bs F_i^{00}\bs M_0^{-1}\bs P_0 \bs 1 -\sum_{j\in\calS_{{-1} }}c_ip_{ij}^{-1} \bs P_0^{-1}\boldsymbol \phi_0(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_0^{-1}(\bs F_i^{0,0}+\bs G_0)\bs M_0^{-1}\bs P_0\boldsymbol 1 
		% \\&= -\sum_{j\in\calS_+} c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 -\sum_{j\in\calS_{{-1} }}c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1\bs 1+ c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1
		% \\&\quad{}+ c_i \bs P_1^{-1}\bs G_1\bs M_1^{-1}\bs P_1\boldsymbol 1
		% %
		% \\&= - c_i \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 + c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1 + c_i \bs P_1^{-1}\bs G_1\boldsymbol 1
		\\&= \bs 0.
	\end{align*}
